---
title: "R Notebook"
output: html_notebook
---

# Notes of R for data science
## Chapter 1

* Basics 

```{r}
library(tidyverse)
ggplot(data=mpg)+geom_point(mapping = aes(x=displ,y=hwy))
```

* Just to add _aesthetics_ to the plot

```{r}
ggplot(data=mpg)+geom_point(mapping = aes(x=displ,y=hwy,color=class))
```

```{r}
ggplot(data = mpg) +
geom_point(mapping = aes(x = displ, y = hwy, size = class))

#transparency of point
ggplot(data = mpg) +
geom_point(mapping = aes(x = displ, y = hwy, alpha = class))

#shape of point
ggplot(data = mpg) +
geom_point(mapping = aes(x = displ, y = hwy, shape = class))

#color is a string
ggplot(data = mpg) +
geom_point(mapping = aes(x = displ, y = hwy), color = "blue")
```

* Facets
Split plots to subplots
```{r}
#facet according to single varaible, facet_wrap(~)
ggplot(data = mpg) +
geom_point(mapping = aes(x = displ, y = hwy)) +
facet_wrap(~ class, nrow = 2)

#facet by two variables, facet_grid(x~y)
ggplot(data = mpg) +
geom_point(mapping = aes(x = displ, y = hwy)) +
facet_grid(drv ~ cyl)
```

* Geometric objects
_Geoms_ are different types of plot:line, bar, scatter...
```{r}
# scatter plot:geom_point
ggplot(data = mpg) +
geom_point(mapping = aes(x = displ, y = hwy))
# line plot:geom_smooth
ggplot(data = mpg) +
geom_smooth(mapping = aes(x = displ, y = hwy))
```

Every _geom function_ of ggplot2 takes a _mapping_ option.

```{r}
ggplot(data=mpg,mapping = aes(x=displ,y=hwy))+
  geom_point(mapping = aes(color=class))+
  geom_smooth(mapping = aes(linetype=drv))
```

* Statistic transformation
  + Bar charts, histograms, and frequency polygons bin your data and then plot bin counts, the number of points that fall in each bin.
  + Smoothers fit a model to your data and then plot predictions from the model.
  + Boxplots compute a robust summary of the distribution and display a specially formatted box.  
```{r}
ggplot(data=diamonds)+
  geom_bar(mapping = aes(x=cut))
```


